---
title: "Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(telegramchatbot)
library(magrittr)
```

## Get an API token

Before anything, you'll need to contact the `@botfather` telegram bot to register your bot and get an API token.
Here's a good [tutorial](https://www.siteguarding.com/en/how-to-get-telegram-bot-api-token) on this if you need additional instructions.

## Answers & Buttons

This bot framework consists of two basic elements: "answers" and "buttons". "Answers" are what the bot sends when the user hits a button or sends a command, and each answer can be followed by one or more buttons that link to other answers.

To build our bot, we first create all the "answers" - all the things that the bot can say:

```{r}

start_answer <- answer(text = "Wecome to this Bot. How are you?")
good_answer <- answer(text = "Glad to hear you're doing well!")
bad_answer <- answer(text = "Sorry to hear.")

```

Now we connect the existing answers via buttons:

```{r}
start_answer <- start_answer %>% 
  add_button(to = good_answer, label = "Good!") %>% 
  add_button(to = bad_answer,  label = "Bad!")

```

So now, the "start_answer" is followed by two buttons labeled "Good!" and "Bad!", which trigger the bot to respond with the text from `good_answer` and `bad_answer` respectively.

Now we can wrap all the answers up in an answer handler:

```{r}
# create a telegram.bot answer handler that monitors what buttons are pressed:

answer_handler <- answer_handler(start_answer, good_answer, bad_answer)

```

## Answering Commands

In terms of commands, at the very least, we need to link the first answer to the `/start` command:

```{r}
start_command <- command("start",answer = start_answer)

```

Let's add another answer to respond to a command, `/about`:

```{r}
about_answer<- answer(text = "this is a simple bot to check in how you are!")

about_comand<-command("about", about_answer)
```

## Start bot

Now we can start the bot!

```{r}
start_bot(Sys.getenv("MANSPLAINBOT_DEV"),
          answer_handler,
          start_command,
          about_comand
          )

```


























